Combined annotation exploration for SCPCP000006

### 2024-11-01 analyses/cell-type-wilms-tumor-06/notebook/07_combined_annotation_across_samples_exploration.Rmd
Include infercnv results for SCPCS000190 by using none as a reference, so we can get some draft annotations for it

# Create a data frames of all annotations
cell_type_df <- unique(metadata$scpca_sample_id) |>
  purrr::map(
    # For each sample_id, do the following:
    \(sample_id) {
      input_file <- file.path(
        result_dir,
        sample_id,
        glue::glue("06_infercnv_HMM-i3_{sample_id}_reference-both.rds")
      )

@@

- Combining label transfer and CNV inference we annotated 38/40 Wilms tumor samples in SCPCP000006. For the two remaining samples, we need to investigate inferCNV further:
    - SCPCS000190 only has 1 normal cell, so we cannot specify a reference for inferCNV
    - SCPCS000203 does not run properly through inferCNV; cells are removed from the inferCNV inference, and why requires further investigation

>>>>

# Create a data frames of all annotations
cell_type_df <- unique(metadata$scpca_sample_id) |>
  purrr::map(
    # For each sample_id, do the following:
    \(sample_id) {
      # This sample was run with "none" for reference
      if (sample_id == "SCPCS000190") {
        reference <- "none"
      } else {
        reference <- "both"
      }
      input_file <- file.path(
        result_dir,
        sample_id,
        glue::glue("06_infercnv_HMM-i3_{sample_id}_reference-{reference}.rds")
      )

@@

- Combining label transfer and CNV inference we annotated 39/40 Wilms tumor samples in SCPCP000006. For the remaining samples (SCPCS000203), we need to investigate inferCNV further, since for some reason inferCNV removes cells from the inference and errors.
